Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-17 manuscript.tex
updates

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 3.6in]{HD12862_gamma_vs_bisspan.pdf} 
\includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. The strong correlation suggests these two parameters are similarly measuring the asymmetry. (top right) RVs as function of Julian Day for Alpha Centauri B in 2010. The RVs are estimated using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan pluses) of a SN density fitted to the CCF. (bottom right) Differences between the RVs estimated with the Normal density and those from the SN density.}
   \label{fig:alphacent:corr.gamma}
\end{center}
\end{figure*}
%

@@

For each of the 4500 simulations we computed the three estimates of RV, namely N mean RV, SN mean RV and SN median RV. 
On each set of RV estimates, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model that includes a 
planet, a non-linear least squares algorithm was used for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
initialised the minimisation algorithm to the real period of the planetary signal injected to avoid getting stuck in a local minimum. We also selected as initial amplitude the peak-to-peak amplitude of the estimated RVs.
The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).

@@

The standard errors were computed for each CCF parameter for the HARPS measurements of HD215152, HD192310 and Corot-7. 
These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent the very low SNR limit and the saturation limit of the HARPS detector, respectively. 
HD10700 and Alpha Centauri B were not included because they have a large number of measurements, which would require a substantial computational effort.
The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
The top row shows the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
The bottom row shows the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller (larger) than one will imply that standard errors from the SN parameters are more (less) precise than the Normal parameters.

>>>>

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 3.6in]{HD12862_gamma_vs_bisspan.pdf} 
\includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{\jessi{needs to be corrected} (left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. The strong correlation suggests these two parameters are similarly measuring the asymmetry. (top right) RVs as function of Julian Day for Alpha Centauri B in 2010. The RVs are estimated using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan pluses) of a SN density fitted to the CCF. (bottom right) Differences between the RVs estimated with the Normal density and those from the SN density.}
   \label{fig:alphacent:corr.gamma}
\end{center}
\end{figure*}
%

@@

For each of the 4590 simulations we computed the three estimates of RV, namely N mean RV, SN mean RV and SN median RV. 
On each set of RV estimates, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model that includes a 
planet, a non-linear least squares algorithm was used for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
initialised the minimisation algorithm to the real period of the planetary signal injected to avoid getting stuck in a local minimum. We also selected as initial amplitude the peak-to-peak amplitude of the estimated RVs.
The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).

@@

The standard errors were computed for each CCF parameter for the HARPS measurements of HD215152, HD192310 and Corot-7. 
These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent the very low SNR limit and the saturation limit of the HARPS detector, respectively. 
HD10700 and Alpha Centauri B were not included because they have a large number of measurements, which would require a substantial computational effort.
The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
The top row shows the standard errors of the three different estimated RVs, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
The bottom row shows the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller (larger) than one will imply that standard errors from the SN parameters are more (less) precise than the Normal parameters.
